Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-20 paper/paper.tex
fix
pass V.E

\subsubsection{Comparison with other tools}\Mar{Lucas and Guilherme,
  please summarize results here!}

\subsubsection{Running time}\Mar{}

>>>>

\subsubsection{Comparison with other tools}
 \Luc{Vollmer \cite{vollmer-etal-cics2011} and Guruprasad \cite{guruprasad} used 
 evolutionaries approaches to 
autonomously generate rules using the Snort IDS. They built 
their own ICMP datasets by using packet creation tools or by capturing network traffic. 
Guruprasad also used DARPA 1999 and ISCX 2012 \cite{iscx} datasets for non-ICMP attacks.

Vollmer created ten different packets to match ten existing rules, and then used 
these packets as input to the rule generation process. As a result, the produced 
rules achieved a 100\% detection rate and produced 3 false positives out of 33k packets.

Guruprasad manually created a set of rules by analyzing the network patterns and 
the datasets, this set of rules was used as the initial population of the algorithm. 
The produced rules achieved a detection rate up to 96\%, the false positive rate 
was not evaluated.

On our experiments with Syrius, we used a total of \totalPackets packets that 
matches \totalAttacks different existing rules and it was able to generate rules that detected 
all the packets with no false positives.  
 }  
\subsubsection{Running time}\Mar{}
